
# About the project

*Write a short description about the course and add a link to your GitHub repository here. This is an R Markdown (.Rmd) file so you should use R Markdown syntax.*

# Introduction

*The installation process of all needed soft wares was a bit complicate, due to my working place has very strict "admin control". But now I have all needed tools so I can roll up my sleeves and start to study the topics of this course. I'm looking forward to get new tools for doing research. I found this course by accidentally when I scrolled the phD courses of UEF. I'm very interested about biostatistics and I really want to get more tools to analyze data.

Please, find here my GitHub diary: https://github.com/lauralappalainen/IODS-project

As a reflection of reading the course book, I felt __relieved__. Previously I have tried to study and learn R by myself and enrolling some _basics of R_ -course, but I didn't get the idea. I feel that the beginner like me, the textbook is excellent: clear and wrote so simple that I think I could understand something. I really need the skills of R so this is very beneficial for me. One thing there was challenging in these "introduction" chapters of the book: for example the pipe %>% was used in examples (in the chapter 2.2.2) before it was even explained (in the chapter 2.4).*

## Installing some packages and testing syntaxes
```{r}
# This is a so-called "R chunk" where you can write R code.

install.packages("tidyverse")
library(tidyverse) # install.packages("tidyverse")
example_data <- read_csv("https://raw.githubusercontent.com/KimmoVehkalahti/RHDS/master/example_data.csv")
View(example_data) # look at the data

library(tidyverse)
gbd_short <- read_csv("https://raw.githubusercontent.com/KimmoVehkalahti/RHDS/master/data/global_burden_disease_cause-year.csv")
View(gbd_short)

```

``` {r}

install.packages("lubridate")
library(lubridate) # install.packages("lubridate")

current_datetime <- Sys.time()
current_datetime

parse_date_time("21:56 04/Nov'23", "%H:%M %d/%b'%Y")

```
*I tried to use (lubridate) package to parse the date as following but didn't succeed. Interestinly, I copied the R chunk from the "pluginfile" found from MOodle and just modify the current date and time.. If some of referees know that I did wrong, please help me :)

```{r}
a <- 103

a

seq(15, 30)

example_sequence <- seq(15, 30)

example_sequence <- example_sequence/2

example_sequence
```
*This was copied from the puginfile, so let's try this same by me..
```{r}
a <- 120

a

seq(50, 75)

example_sequence <- seq(50,75)

example_sequence <- example_sequence/5

example_sequence

```
*Hoorray, I create something correctly by myself!!

### Summary of week 1 assignment
*This was pretty good way to get in the tools and softwares we will use during this course. Even first steps were uncertain and I felt a bit horrified, now I feel more comfortable, even I'm very beginner with R. Hopefully, this spirit continues :)

Best,
Laura